### 2017-01-24 archive/latex/dir_68267d1309a1af8e8297ef4c3efbcdba.tex
2017/01/24

\hypertarget{dir_14807827589b339a04434892d1c1deae}{}\section{code/src Directory Reference}
\label{dir_14807827589b339a04434892d1c1deae}\index{code/src Directory Reference@{code/src Directory Reference}}
\subsection*{Directories}
\begin{DoxyCompactItemize}
\item 
directory \hyperlink{dir_86633d98051024a4283a8055eb45f008}{common}
\end{DoxyCompactItemize}
\subsection*{Files}
\begin{DoxyCompactItemize}
\item 
file \hyperlink{test_8h}{test.\+h}
\item 
file \hyperlink{validate_8cpp}{validate.\+cpp}
\item 
file \hyperlink{validate_8h}{validate.\+h}
\begin{DoxyCompactList}\small\item\em first method for validating suffix and L\+CP arrays \end{DoxyCompactList}\item 
file \hyperlink{validate2_8cpp}{validate2.\+cpp}
\item 
file \hyperlink{validate2_8h}{validate2.\+h}
\begin{DoxyCompactList}\small\item\em validate sa and lcp using internal memory sorts and Karp-\/rabin finger-\/print function. \end{DoxyCompactList}\item 
file \hyperlink{validate3_8cpp}{validate3.\+cpp}
\item 
file \hyperlink{validate3_8h}{validate3.\+h}
\begin{DoxyCompactList}\small\item\em validate sa and lcp using external memory sorts and Karp-\/rabin finger-\/print function. \end{DoxyCompactList}\item 
file \hyperlink{validate4_8cpp}{validate4.\+cpp}
\item 
file \hyperlink{validate4_8h}{validate4.\+h}
\begin{DoxyCompactList}\small\item\em A two-\/phase validator for suffix and L\+CP arrays verification. \end{DoxyCompactList}\end{DoxyCompactItemize}

>>>>

\hypertarget{dir_68267d1309a1af8e8297ef4c3efbcdba}{}\section{src Directory Reference}
\label{dir_68267d1309a1af8e8297ef4c3efbcdba}\index{src Directory Reference@{src Directory Reference}}
\subsection*{Directories}
\begin{DoxyCompactItemize}
\item 
directory \hyperlink{dir_fdedb0aba14d44ce9d99bc100e026e6a}{common}
\end{DoxyCompactItemize}
\subsection*{Files}
\begin{DoxyCompactItemize}
\item 
file \hyperlink{test_8h}{test.\+h}
\item 
file \hyperlink{validate_8cpp}{validate.\+cpp}
\item 
file \hyperlink{validate_8h}{validate.\+h}
\begin{DoxyCompactList}\small\item\em first method for validating suffix and L\+CP arrays \end{DoxyCompactList}\item 
file \hyperlink{validate2_8cpp}{validate2.\+cpp}
\item 
file \hyperlink{validate2_8h}{validate2.\+h}
\begin{DoxyCompactList}\small\item\em validate sa and lcp using internal memory sorts and Karp-\/rabin finger-\/print function. \end{DoxyCompactList}\item 
file \hyperlink{validate3_8cpp}{validate3.\+cpp}
\item 
file \hyperlink{validate3_8h}{validate3.\+h}
\begin{DoxyCompactList}\small\item\em validate sa and lcp using external memory sorts and Karp-\/rabin finger-\/print function. \end{DoxyCompactList}\item 
file \hyperlink{validate4_8cpp}{validate4.\+cpp}
\item 
file \hyperlink{validate4_8h}{validate4.\+h}
\begin{DoxyCompactList}\small\item\em A two-\/phase validator for suffix and L\+CP arrays verification. \end{DoxyCompactList}\end{DoxyCompactItemize}

### 2017-01-24 archive/latex/dir_fdedb0aba14d44ce9d99bc100e026e6a.tex
2017/01/24

\hypertarget{dir_86633d98051024a4283a8055eb45f008}{}\section{code/src/common Directory Reference}
\label{dir_86633d98051024a4283a8055eb45f008}\index{code/src/common Directory Reference@{code/src/common Directory Reference}}
\subsection*{Files}
\begin{DoxyCompactItemize}
\item 
file \hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h}
\begin{DoxyCompactList}\small\item\em read elements from disk file using asychronous I/O operations \end{DoxyCompactList}\item 
file \hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h}
\begin{DoxyCompactList}\small\item\em write elements into disk file using asynchronous I/O operations. \end{DoxyCompactList}\item 
file \hyperlink{basicio_8h}{basicio.\+h}
\begin{DoxyCompactList}\small\item\em provide basic I/O interface for sequential read/write operations \end{DoxyCompactList}\item 
file \hyperlink{common_8h}{common.\+h}
\begin{DoxyCompactList}\small\item\em definition of macro, constant and alias for common use \end{DoxyCompactList}\item 
file \hyperlink{namespace_8h}{namespace.\+h}
\item 
file \hyperlink{tuples_8h}{tuples.\+h}
\item 
file \hyperlink{types_8h}{types.\+h}
\begin{DoxyCompactList}\small\item\em definition of namespace \end{DoxyCompactList}\item 
file \hyperlink{widget_8h}{widget.\+h}
\begin{DoxyCompactList}\small\item\em sort elements in external memory \end{DoxyCompactList}\end{DoxyCompactItemize}

>>>>

\hypertarget{dir_fdedb0aba14d44ce9d99bc100e026e6a}{}\section{src/common Directory Reference}
\label{dir_fdedb0aba14d44ce9d99bc100e026e6a}\index{src/common Directory Reference@{src/common Directory Reference}}
\subsection*{Files}
\begin{DoxyCompactItemize}
\item 
file \hyperlink{async__stream__reader_8h}{async\+\_\+stream\+\_\+reader.\+h}
\begin{DoxyCompactList}\small\item\em read elements from disk file using asychronous I/O operations \end{DoxyCompactList}\item 
file \hyperlink{async__stream__writer_8h}{async\+\_\+stream\+\_\+writer.\+h}
\begin{DoxyCompactList}\small\item\em write elements into disk file using asynchronous I/O operations. \end{DoxyCompactList}\item 
file \hyperlink{basicio_8h}{basicio.\+h}
\begin{DoxyCompactList}\small\item\em provide basic I/O interface for sequential read/write operations \end{DoxyCompactList}\item 
file \hyperlink{common_8h}{common.\+h}
\begin{DoxyCompactList}\small\item\em definition of macro, constant and alias for common use \end{DoxyCompactList}\item 
file \hyperlink{namespace_8h}{namespace.\+h}
\item 
file \hyperlink{tuples_8h}{tuples.\+h}
\item 
file \hyperlink{types_8h}{types.\+h}
\begin{DoxyCompactList}\small\item\em definition of namespace \end{DoxyCompactList}\item 
file \hyperlink{widget_8h}{widget.\+h}
\begin{DoxyCompactList}\small\item\em sort elements in external memory \end{DoxyCompactList}\end{DoxyCompactItemize}
